\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, physics}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{a4paper, margin=1in}

\title{Physics and Mathematics of Holland-Burnett State Initialization and Metrology Metrics}
\author{A Theoretical Review}
\date{\today}

\begin{document}
\maketitle

\section*{Overview}
This notebook structure evaluates Holland-Burnett (HB) states tracking Quantum Fisher Information (QFI) against absolute physical boundaries over specific noisy parameters. Our evaluation maps limits of $N$ photon signals subjected to $d$ phases, computing performance drops over probabilistic shared vs. independent noise distributions ($p, \eta$) effectively.

---

\section*{Cell 1: Imports and Dependencies}
Initializes matrix arrays efficiently utilizing Pandas mapping and \texttt{qutip} frameworks dynamically. Necessary tools including \texttt{tensor}, \texttt{qeye}, \texttt{basis}, and \texttt{ket2dm} set up vector mathematics tracking quantum evolutions natively instead of analytically guessing structures.

\section*{Cell 2: The Core Physics Engine}

\subsection*{2.1 Quantum Fisher Information Matrix (QFIM)}
The Symmetric Logarithmic Derivative (SLD) $L_{\mu}$ governs the matrix geometry necessary to derive Cramer-Rao boundaries (CRB). For a state $\rho$ subject to phase displacement estimations $U(\boldsymbol{\theta}) = \exp(-i \sum_{\mu} \hat{n}_{\mu} \theta_{\mu})$, the partial derivative evaluated at the phase origin implies:
\begin{equation}
    \partial_\mu \rho \Big|_{\boldsymbol{\theta} = 0} = -i [\hat{n}_\mu, \rho]
\end{equation}
To calculate this practically, we resolve $\rho$ into its spectral eigenbasis: $\rho = \sum_k \lambda_k |k\rangle\langle k|$. Consequently, the partial derivative map transitions analytically to:
\begin{equation}
    \langle k | \partial_\mu \rho | m \rangle = -i(\lambda_m - \lambda_k)\langle k | \hat{n}_\mu | m \rangle
\end{equation}
In our codebase (seen precisely in \texttt{compute\_rho\_derivative}), this manifests by establishing matrices for eigenvalue variations evaluated natively. Proceeding forward, the QFIM bridges from the derivatives:
\begin{equation}
    F_{\mu\nu} = \operatorname{Re}\left(  \sum_{\lambda_m + \lambda_k > 0} \frac{2}{\lambda_n + \lambda_m} \langle k| \partial_\mu \rho |m\rangle \langle m| \partial_\nu \rho | k\rangle \right)
\end{equation}
This bounds identically the multiple independent phases' ultimate precision evaluated as standard Cramer-Rao variance:
\begin{equation}
    \Delta^2 (\hat{\boldsymbol{\theta}}) \geq \operatorname{Tr}\left(\mathcal{F}^{-1}_{\boldsymbol{\theta}}\right)
\end{equation}

\subsection*{2.2 The Noise Channel ($\mathcal{N}_{\text{tot}}$)}
The beam-splitter simulation models practical photonic damping (loss mechanism mapping to non-unity transmissivity $\eta$). The Stinespring dilation interaction linking our active signal modes $\hat{a}_S$ against surrounding reservoir vacuums $\hat{a}_E$:
\begin{equation}
    \hat{V} = \exp\left[\theta_{\text{int}}\left( \hat{a}_S^\dagger \hat{a}_E - \hat{a}_S \hat{a}_E^\dagger \right)\right] 
\end{equation}
Under standard transformations, mapping relates mathematically to evaluating $\cos^2(\theta_{\text{int}}) = \eta$, ensuring $\theta_{\text{int}} = \arccos(\sqrt{\eta})$. 

The script parses this globally against two distinct decoherence profiles linked directly to a mixing probability $p$:
\begin{itemize}
    \item \textbf{Independent Error ($\mathcal{N}_{\text{free}}$)}: Distributes exclusive independent vacuum ancillary channels against sequentially unlinked operators per each signal register $i \in K$.
    \item \textbf{Correlated Noise ($\mathcal{N}_{\text{int}}$)}: Operates globally over synchronized phase loss wherein all parallel phase registers route unitarily against a single shared environment entity.
\end{itemize}

\section*{Cell 3: State Initialization Equations}

\subsection*{3.1 The Holland-Burnett State ($|\psi_{HB}\rangle$)}
Standard initialization bounds map $N$ resources globally over $d$ phases, extending fundamentally into $d+1$ total components (registering signal versus reference spaces). 
The $HB(n, d)$ architecture explicitly deposits identical particle distributions $n=N/(d+1)$ targeting respective ports of a multiport Quantum Fourier Transform (QFT) interferometer gate.
We construct dynamic transformed creation structures via:
\begin{equation}
    \hat{b}_k^{\dagger} = \frac{1}{\sqrt{d+1}}\sum_{j=0}^d e^{i\frac{2\pi}{d+1}j \cdot k} \, \hat{a}_j^{\dagger}
\end{equation}
Resulting mathematically over vacuum applications:
\begin{equation}
    |\psi_{HB}\rangle \propto (\hat{b}_0^\dagger)^n (\hat{b}_1^\dagger)^n \dots (\hat{b}_d^\dagger)^n |0\rangle^{\otimes d+1} 
\end{equation}
Resolving specifically $N=3$, $d=2$ yields mathematically the output proxy matching purely derived state symmetries expanding algebraically to distributions resolving exclusively the limits.

\subsection*{3.2 The Reference Bound State ($|\psi_s\rangle$)}
Evaluating directly the theoretical peak established natively in Humphreys Equation 8 optimally minimizing variance bounding Equation 10 limit:
\begin{equation}
    |\psi_S\rangle = \beta|0_{\text{sig}}\rangle \otimes |N_{\text{ref}}\rangle + \alpha \sum_{j=1}^d |N^{(j)}_{\text{sig}}\rangle \otimes |0_{\text{ref}}\rangle
\end{equation}
Where mathematically evaluating the scale amplitude yields exact derivations isolating optimal components:
\begin{equation}
    \alpha = \frac{1}{\sqrt{d+\sqrt{d}}} \quad \text{and} \quad \beta = \frac{1}{\sqrt{1+\sqrt{d}}}
\end{equation}
These arrays pass unitarily directly as exact numerical kets resolving fidelity approximations evaluated inside our matrices computationally.

\section*{Cell 4: Metric Evaluation and Layout Logic}
This section handles plotting matrices formatting Cramer-Rao boundaries natively against $p$ scales. 
Instead of optimizing, we plot identically our statically parsed states over grids. 
We establish analytical values:
\begin{itemize}
    \item \textbf{Standard Quantum Limit (SQL)} scales $\approx d^2 / N$ for total combined variance scales efficiently.
    \item \textbf{Heisenberg NOON Bound} scales $\approx d^3 / N^2$. 
    \item \textbf{Humphreys Ideal Multipixel Eq 10 Limit} natively maps $\approx \frac{d(1+\sqrt{d})^2}{4N^2}$.
\end{itemize}

\section*{Cell 5: Global Execution Block}
Combines states from Cell 3, evaluates grids from Cell 2 traces spanning ranges of independent vs shared mixtures ($p$) and tracks plotting maps from Cell 4 automatically to visualize exactly evaluated footprints. Initial calculations compute exactly $Fidity = |\langle \psi_{HB} | \psi_{s} \rangle|^2 $.

\end{document}
